Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-15 ms.rmd
Fix grammar error, and also removed some code and added het models for traits to do AIC comparison

After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions. In all models, we included the same random effects as we used in our MLMA models. Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`). Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$. To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models. As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).

@@

  # Check whether there is differences in variances for each habitat
  model1.2_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 + habitat | obs),
                              R = list(species_full = phylo_cor), struct = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

@@

    # Filter out antioxidant
  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
   # Prune tree
   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")

@@

  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")

  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")

>>>>

After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions. In all models, we included the same random effects as we used in our MLMA models. Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`). Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$. To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models. As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).

@@

@@

    # Filter out antioxidant and NAs
  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time))

  # Prune tree
   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")

@@

  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
   saveRDS(model1.3_f_het, file = "./output/models/lnRRQ10_1.3f_het")
  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")

  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
   saveRDS(model1.3_t_het, file = "./output/models/lnRRQ10_1.3t_het")
  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")
